---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 90)
library(googler)
```

# googler

<!-- badges: start -->
<!-- badges: end -->

This is a wrapper around the ['googler' command line tool](https://github.com/jarun/googler).

## Requirements

Python3 must be installed and located with the following code:

``` r
Sys.which("python3")
```


## Installation

You can install the development version of {googler} from [Github](https://github.com/mkearney/googler) with:

``` r
remotes::install_github("mkearney/googler")
```

<!-- You can install the released version of googler from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("googler") -->
<!-- ``` -->

## Examples

Search google with various options to specify things like the desired result **`count`**, google **`news`**, within a range of **`time`**, from a given **`site`**, etc.

### Example #1: `googler()`

```{r}
## search google for 'rstats'
googler("rstats")

## search google for 100 'rstats' or "R language" hits in past year
googler("rstats OR \"R language\"", count = 100, time = "y1")
```

### Example #2: `googler()`

```{r}
## search google news for rstats/R language articles in the past three weeks
googler("rstats OR \"R language\"", news = TRUE, time = "w3", exact = TRUE)
```

